Efficiently summarizing relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-19 treestats_paper.tex
added ratio to relate

\begin{figure}
    \includegraphics{{figures/1kg/relate_chr20.site.1000000.region.diversity}.pdf}
    \includegraphics{{figures/1kg/relate_chr20.branch.1000000.region.diversity}.pdf}
    \caption{
        \textbf{(top)} Mean sequence diversity
        in 1Mb windows along human chromosome 20 of the 1000 Genomes Project,
        in units of mean number of pairwise differences per nucleotide,
        and \textbf{(bottom)}
        the dual Branch statistic as calculated from tree sequences inferred by
        Relate~\citep{speidel2019method},
        in units of generations.
        Separate curves are plotted for each sampling location.
        \label{fig:chr20}
    }
\end{figure}

@@

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{{figures/swept.10000.765.1e-09.diversity}.pdf}
    \caption{
        As in Figure~\ref{fig:sweep_duality}, but in a population of size 10,000.
        \label{sfig:sweep_duality_10K}
    }
\end{figure}

>>>>

\begin{figure}
    \includegraphics{{figures/1kg/relate_chr20_site_div_branch.1000000.diversity}.pdf}
    \caption{
        \textbf{(top)} Mean sequence diversity
        in 1Mb windows along human chromosome 20 of the 1000 Genomes Project,
        in units of mean number of pairwise differences per nucleotide.
        \textbf{(middle)}
        The dual Branch statistic as calculated from tree sequences inferred by
        Relate~\citep{speidel2019method},
        in units of generations.
        \textbf{(bottom)} The ratio of the Site statistic to the Branch statistic,
        which note hovers around typical per-generation estimates of the human mutation rate.
        Separate curves are plotted for each sampling location.
        \label{fig:chr20}
    }
\end{figure}

@@

\begin{figure}[!h]
    \includegraphics[width=\textwidth]{{figures/swept.10000.765.1e-09.diversity}.pdf}
    \caption{
        As in \autoref{fig:sweep_duality}, but in a population of size 10,000.
        \label{sfig:sweep_duality_10K}
    }
\end{figure}
